---
title: "Project Summary"
author: "Daniel Tan"
date: "24 August 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('data_prep3.R')
source('forecast2.R')

train <- read.train()
test <- read.test()
mts <- master.ts(train)
```

## Background

In 2014, Walmart held a Kaggle competition to challenge Kagglers to build an accurate prediction of future sales based on historical data.


I have chosen a scoped down version of this competition as my Springboard Capstone Project. If you would like to see the full details of the original Kaggle competition, please visit [this link](https://www.kaggle.com/c/walmart-recruiting-store-sales-forecasting).

## 1. Data Preparation

I begin with 2 datasets:

* __train.csv__: Historical training data from 5/2/2010 to 26/10/2011, containing Store number, Department number, Date of the week, Weekly sales figure and isHoliday boolean

* __test.csv__: Test data for 2/11/2012 to 26/7/2013, containing collumns for Store, Department, Date and IsHoliday

```{r, echo=TRUE}
# Snippet of train data
train

# Snippet of test data
test
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
